
\chapter*{ABSTRACT}
\vspace*{0.7cm}

Many selection models are carried out in order to assess someone, especially when a company seeks positions such as by conducting an assessment center and filling out an assessment form for each candidate to be nominated as a leader and staff. Many procedures and conditions must be had by prospective leaders and staff, be it managers or division heads and staff. Every person chosen means fulfilling the conditions set by the company. Provisions are made based on the competence of each section compiled in the company competency dictionary. Through the competency dictionary, it can also be used as a guideline for the Human Resources section in looking for high-potential employees for the sustainability of the company. There is a problem that there is no mechanism for determining the right candidate, if there is a position that is replaced or vacant. Then there is no employee data that will be used as a candidate to fill the replaced or vacant position.
\\

To overcome the above problems, the application design "\textbf{SiPJabS: Structural Position Management System at Telkom University}" aims to improve the career management process. So that the organization or company gets a high quality. By providing more competitive and fair application. Then it can also analyze risks, for example identification of employees who have the potential to leave. Then it can improve learning and development programs for performance and develop better competencies in the future.

\noindent \textbf{Keywords:} Employees, Recruitment, Companies\\ 

\newpage